### 2015-11-17 Irregular-occ/Irregular-occ.tex
Iniciado mudancas sugeridas pela Laurene

\abstract
{Due to their orbital configurations, it is common belief that the irregular satellites were probably captured by the giant planets in the early solar system. It is important to know their physical parameters, such as size and albedo, to trace back their true origin. The best ground-based technique to obtain such parameters is the observation of stellar occultations by these objects.}
{We aimed to predict stellar occultations for the seven biggest irregular satellites of Jupiter: Himalia, Elara, Pasiphae, Carme, Lysithea, Sinope and Ananke; for the irregular satellite of Saturn: Phoebe; and the satellites of Neptune: Nereid and Triton.}
{We identified candidates to stellar occultations by the irregular satellites from the UCAC4 catalogue and from a catalogue of stars in the sky-path of Neptune obtained from observations made with the ESO2p2/WFI (2.2 m Max-Planck ESO telescope with the Wide Field Imager) instrument. These catalogues were crossed with the ephemeris of the satellites to identify stellar occultations. The ephemeris were generated by a numerical integration \textcolor{red}{(Here we may write something about after the work of Laurène)} that used the positions obtained by \cite{GomesJunior2015} to improve the predictions.}
{We managed to obtain \textcolor{red}{588} candidates of stellar occultations between the period of January, 2015 and December, 2017. We made observational tests for the predictions of the events of Himalia in March 03, 2015 and Elara in March 30, 2015. The observations were made in the same field to minimize errors and the obtained relative satellite-star positions were used to evaluate the predictions.}
{The comparisons between the predictions and the observation tests show a good agreement. We discuss how the successful observation of a stellar occultation by these objects is quite possible.}

@@

Irregular (outer) satellites revolve around giant planets at large distances in eccentric, highly inclined and frequently retrograde orbits. Because of these peculiar orbits, it is largely accepted that these objects were not originated with, but were captured by their planets in the early solar system \citep{Sheppard2005}.

There is a number of capture mechanisms of objects by giant planets proposed in the literature. There is the Gas Drag in the primordial circumplanetary nebulae \citep{Sheppard2005} where the object would be affected by the gas drag and its velocity slowed down until it be captured by the planet. Another mechanism is called pull-down capture \citep{Sheppard2005}, where the mass of the planet would increase while the object was temporarily captured.

A mechanism based in the Nice model \citep{Morbidelli2005, Tsiganis2005, Gomes2005} was proposed by \cite{Nesvorny2007} and, in the specific case of Jupiter with the modern Nice model, by \citealp{Nesvorny2014}. During the early solar system instability, encounters between the outer planets occurred. These planetary encounters could exchange energy and angular momentum between planets and the objects nearby making it possible for the capture of irregular bodies by the giant planets. In this scenario, the survival rate of prior-LHB (Late Heavy Bombardment) satellites is very small.

Another important mechanism is the capture through collisional interactions \citep{Sheppard2005}. A collision between two small bodies in the Hill's sphere of the planet could generate fragmented objects and the dissipated energy could be such that some of these objects could be captured.

Some of these objects are in dynamical groups with similar orbital elements, called families, similar to families found in the Main Asteroid Belt. These families may have been created by a parent body disrupted by collisions with comets or other satellites \citep{Nesvorny2004}. Collisions with comets are more likely to have occurred during the LHB \citep{Gomes2005}.

@@

For Phoebe, ejected material from its surface caused by impacts could evolve due to Poynting-Robertson drag and collide with Iapetus causing the large variation in albedo observed on it \citep{Nesvorny2003}. Indeed, Cassini was able to detected in Phoebe an absorption feature at 2.42 $\mu m$ (probably CN combinations) that was also detected in the dark side of Iapetus \citep{Clark2005}.

The region of origin of these object is not well known. \cite{Grav2003} and \cite{Grav2007} showed that the irregular satellites from the giant planets have their colors and spectral slopes similar to C-, D- and P-type asteroids, Centaurs and trans-neptunian objects (TNOs) suggesting that they have been originated from different locations in the early solar system.

In order to obtain precise fundamental physical parameters like size, shape and albedo for the irregular satellites and thus to contribute to the study of their origin, we will make use of stellar occultations, which provide  more accurate results than other ground-based techniques \citep{Sicardy2011, Ortiz2012, Braga-Ribas2014}.

No observation of a stellar occultation by an irregular satellite was published up to date. Since their estimated sizes are very small (see Table \ref{Tab: satellite-diameter}), this may have prevented earlier tries. But, in fact, given their distances to us, current ephemeris and star positions are already good enough for the prediction of the exact location and instant where the shadow of the occultation will cross the Earth. For instance, Himalia, supposedly the largest irregular satellite of Jupiter has an estimated size of 150 km \citep{Porco2003}, which is equivalent to an apparent size of about 40 mas (milliarcseconds).Thus, in this case, the overall budget of ephemeris and star position errors must be around 40 mas in order that we get good chances of observing a stellar occultation, which is quite feasible today.

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{centering}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & km  & mas\tablefootmark{a} & References \tabularnewline
\hline
Ananke & 29 & 8 & 1 \tabularnewline
Carme & 46 & 13 & 1 \tabularnewline
Elara & 86 & 24 & 1 \tabularnewline
Himalia & $(150\times120) \pm 20$\tablefootmark{b} & 41 & 2 \tabularnewline
Lysithea & 36 & 10 & 1 \tabularnewline
Pasiphae & 62 & 17 & 1 \tabularnewline
Sinope & 37 & 10 & 1 \tabularnewline
\hdashline
Phoebe & $212 \pm 1.4$\tablefootmark{b} & 32 & 3 \tabularnewline
\hdashline
Nereid & $340 \pm 50$\tablefootmark{c} & 15 & 4 \tabularnewline
Triton & $2707 \pm 2.0$\tablefootmark{c} & 124 & 5 \tabularnewline
\hline
\end{tabular}
\tablebib{
(1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}; (4) \cite{Thomas1991}; (5) \cite{Thomas2000}.}
\end{centering}
\tablefoottext{a}{Using a mean distance from Jupiter of 5 AU, from Saturn of 9 AU and from Neptune of 30 AU.}
\tablefoottext{b}{From Cassini observation.}
\tablefoottext{c}{From Voyager-2 observation.}
\par
\end{table}

Unlike stellar occultations by TNOs, which nevertheless have been proved effective, the observation of an occultation by a irregular satellite is, in principle, more favorable. The orbits of their host planets are well known and these satellites have been observed completing already many orbital periods around them, thus presenting better ephemeris than TNOs. Moreover, the irregular satellites are closer to Earth which means a minor location error in kilometers.

\cite{GomesJunior2015} obtained 6523 suitable positions for 18 irregular satellites between 1992 and 2014 with an estimated error in the positions of about 60 to 80 mas. For some satellites the number of positions obtained is comparable to the number used in the numerical integration of orbits by the JPL \citep{Jacobson2012}. They pointed out that the ephemeris of the irregular satellites have systematic errors that may reach 200 mas for some satellites. For an object at the distance of Jupiter, this represents an error bigger than 700 km in the shadow path. Using the positions obtained by \cite{GomesJunior2015} it is possible to improve the ephemeris and better predict stellar occultations for these objects.

We present in this paper stellar occultation predictions for the 7 major irregular satellites of Jupiter (Himalia, Elara, Pasiphae, Lysithea, Carme, Ananke and Sinope), Phoebe from Saturn and Nereid and Triton from Neptune. In the section \ref{Sec: Rationale} we explore the scientific rationale for the study of the irregular satellites and the possibility of having a common origin with TNOs. In section \ref{Sec: Offset} we show the \textcolor{red}{numerical integration to improve the ephemeris}. In section \ref{Sec: predictions}, we present the predictions of the stellar occultations by irregular satellites and how they were made. Some tests made to confirm the predictions are presented in section \ref{Sec: testes} and the conclusions are given in section \ref{Sec: conclusions}.

@@

Phoebe is the most studied irregular satellite. \cite{Clark2005} suggest that its surface is probably covered by material of cometary origin. It was also stated by \cite{Johnson2005} that if the porosity of Phoebe would be of about 15\%, which the authors believe it is possible, Phoebe would have an uncompressed density similar to those of Pluto and Triton.

\cite{Sheppard2005} and \cite{Jewitt2007} also expose the possibility for the irregular satellites having their origin as comets or similar to the TNOs. TNOs are highly interesting objects that due to their large heliocentric distances (low temperatures) may be highly preserved having their physical properties similar to those they had when they were formed, then providing history and evolution of the outer solar system \citep{Camargo2014}. This is even more true for the smaller objects, since in principle larger sizes favour physical differentiation processes in the body and vice-versa. However, due to the distance, the smaller TNOs from this region are more difficult to observe. A clever way to overcome this difficulty is to study  the much closer irregular satellites, under the hypothesis that they share a common origin with the small TNOs' population.

Triton is a special satellite. Its orbit is retrograde and inclined, but quasi-circular and very close to the planet compared to the irregular ones. Because Triton's orbit size is very small and its precession is not dominated by Solar perturbations, Triton is frequently excluded from the irregular satellites' class, but studied together by many authors \citep{Sheppard2005, Jewitt2007}.

Similarly to the irregular satellites, Triton was probably captured in the early solar system and may have a similar origin as the TNOs \citep{Agnor2006}. Differently, Triton is bigger than the irregular satellites by an order of magnitude and has an atmosphere. The main motivation here to study Triton by stellar occultations is to understand the evolution of its atmosphere due to Triton's complicated and extreme seasonal cycle \citep{McKinnon2007}.

@@

\section{Correction of the ephemeris} \label{Sec: Offset}

@@

All the orbits determined for the satellites show satisfying residuals. Yet, one of the satellites has a peculiar situation. Its small number of observations in our set means that its orbit is definitely loosely constrained. 
The residuals are lower than those obtained with JPL ephemeris, but the accuracy of an ephemeris decreases when we get further from the time of observations. The main risk of divergence over time comes from the possible absence of long-term effects when fitting to a short timespan of observations. If that were the case, our ephemeris would diverge too quickly to be of any use. JPL ephemerides are fitted over all the available observations. As a result, they will diverge less quickly than our own. Though they are no longer precise enough for our use, they remain a recious reference to identify whether our own model presents a quick divergence. We compared our ephemeris to the JPL for all the Jupiter satellites we fitted, until 2017. The divergence between 2015 and 2018 is at most \textit{\color{red}insert value here} for \textit{\color{red}insert right satellite name here}. A example of this difference for satellites Himalia and \textit{\color{red}whichever satellite you want, if you want)} is presented in Figure \ref{JPL-STE}.

@@

\begin{table*}
\caption{Initial osculating elements for Jupiter irregular satellites at JD 2451545.0. For Themisto's case, the small number of observations meant that the statistical uncertainty was even greater than the obtained elements, though the fitting proved satisfying. We decided to provide its elements with significant number comparable to the other satellite for information, but left it without uncertainty.  }\label{Tab: sat_ell}
\begin{center}
\begin{tabular}{ccccccc}
\hline\hline
Satellite & a (km) & e & incl. (EQJ2000) & $\Omega$ & $\omega$ & $v$ \\ 
\hline
Himalia &   11372100 $\pm$ 500    &    0.166 $\pm$ 0.002      &   45.14 $\pm$ 0.15      &   39.77 $\pm$ 0.19      &   351.48 $\pm$ 0.46      &   97.35 $\pm$ 0.48    \\
Elara &   11741170 $\pm$ 690  &      0.222 $\pm$ 0.002      &   28.64 $\pm$ 0.18      &   68.42 $\pm$ 0.43      &   179.82 $\pm$ 0.56      &   339.08 $\pm$ 0.82  \\
Pasiphae &  23425000  $\pm$ 5000    &     0.379  $\pm$ 0.001       &   152.44 $\pm$ 0.10      &   284.59 $\pm$ 0.21      &   135.96 $\pm$ 0.19      &   236.97 $\pm$ 0.16 \\
Sinope &   22968800 $\pm$ 5200   &     0.316 $\pm$ 0.002      &   157.76 $\pm$ 0.12      &   256.62 $\pm$ 0.55      &   298.38 $\pm$ 0.55      &   167.57 $\pm$ 0.19    \\
Lysithea &   11739900 $\pm$ 1300  &      0.136 $\pm$ 0.004      &    51.12 $\pm$ 0.27     &   5.53 $\pm$ 0.52      &   53.0 $\pm$ 1.5      &   318.9 $\pm$ 2.0   \\
Carme &   24202924 $\pm$ 4800      &  0.242 $\pm$ 0.001      &   147.13 $\pm$ 0.10      &   154.01 $\pm$ 0.25      &   47.90 $\pm$ 0.29      &   234.41 $\pm$ 0.19  \\
Ananke &  21683800  $\pm$ 7200  &     0.380 $\pm$ 0.002      &   172.29 $\pm$ 0.20      &   56.9 $\pm$ 1.2      &   123.3 $\pm$ 1.2      &   231.24 $\pm$ 0.21  \\
Leda &   11140300  $\pm$ 4300  &     0.173  $\pm$ 0.007     &   16.15  $\pm$ 0.75    &   272.6  $\pm$ 1.7    &   212.2  $\pm$ 3.6          &   218.8  $\pm$ 3.2  \\
Themisto  & 7393800    &     0.198       &   25.77  &   220.0     &   216.3    &   262.1     \\ \hline
\end{tabular}

\end{center}
\end{table*}
%\cite{GomesJunior2015} published 6523 precise positions for 18 irregular satellites from observations made at the Observatório do Pico dos Dias (OPD), Observatoire Haute-Provence (OHP) and European Southern Observatory (ESO) between 1992 and 2014. They showed that the orbits of the irregular satellites of the giant planets have systematic errors. The offsets of the observations relative to the JPL ephemeris could be up to 200 mas for some satellites. These differences could be associated with errors in their orbital elements.

@@

\begin{figure*}
\begin{centering}
\subfigure[Offset from the JPL ephemeris]{\includegraphics[width=8.8cm]{figures/DEC_anom.png} \label{Fig:offxtanomxjpl}}
\subfigure[\textcolor{red}{Offset from the numerical integration}]{\includegraphics[width=8.8cm]{figures/DEC_anom.png} \label{Fig:offxtanomxni}}
\caption{Offsets of the declination of Carme by true anomaly from the JPL ephemeris and \textcolor{red}{from the numerical integration of the positions obtained in \cite{GomesJunior2015}}.
\label{Fig:offxanom}}
\end{centering}
\end{figure*}

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the corrected JPL ephemeris as presented in section \ref{Sec: Offset}. The search for stellar candidates follows the same procedure as presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2014}.

@@

A total of 588 events \textcolor{red}{(Not counting Triton's event yet)} were identified between January 2015 and December 2017. Table \ref{Tab: occ-list} exemplifies the catalogue of occultations generated and their parameters, which are necessary to produce occultation maps (see Fig. \ref{Fig: ocultacao} as an example). Since these objects are very small, the duration of each event is a few seconds.

>>>>

\abstract
{Due to their orbital configurations, it is common belief that the irregular satellites were probably captured by the giant planets in the early solar system. It is important to know their physical parameters, such as size, albedo and composition, to trace back their true origin. The best ground-based technique to constrain those parameters is the observation of stellar occultations by these objects.}
{We aim to predict stellar occultations for the seven biggest irregular satellites of Jupiter: Himalia, Elara, Pasiphae, Carme, Lysithea, Sinope, Ananke and Leda; the irregular satellite of Saturn: Phoebe; and the satellites of Neptune: Nereid and Triton.}
{We identified candidates to stellar occultations by the irregular satellites from the UCAC4 catalogue and from a catalogue of stars in the sky-path of Neptune obtained from observations made with the ESO2p2/WFI (2.2 m Max-Planck ESO telescope with the Wide Field Imager) instrument. These catalogues were crossed with the ephemeris of the satellites to identify stellar occultations. We used a new ephemeris based solely on the observations from \cite{GomesJunior2015} to generate quick predictions for the short-time future for the satellites of Jupiter. For Phoebe, Nereid and Triton we used the JPL ephemeris.}
{We managed to obtain \textcolor{red}{588} candidates of stellar occultations between the period of January, 2015 and December, 2017. We made observational tests for the predictions of the events of Himalia in March 03, 2015 and Elara in March 30, 2015. The stars and objects were observed close to the date predicted and and in the same field to minimize errors and the obtained relative satellite-star positions were used to evaluate the predictions.}
{The comparisons between the predictions and the observation tests show a good agreement. We discuss how the successful observation of a stellar occultation by these objects is quite possible and present some of those potential occultations.}

@@

Irregular satellites revolve around giant planets at large distances, on eccentric, highly inclined and frequently retrograde orbits. Because of these peculiar orbits, it is largely accepted that these objects did not form by accretion around of their planet, but were captured by their planets in the early solar system \citep{Sheppard2005}.

There are several of capture mechanisms of objects by giant planets suggested in the literature. For example the Gas Drag in the primordial circumplanetary nebulae \citep{Sheppard2005} where the object would be affected by the gas drag and its velocity slowed down until it be captured by the planet. Another mechanism is called pull-down capture \citep{Sheppard2005}, where the mass of the planet would increase while the object was temporarily captured.

A mechanism based in the Nice model \citep{Morbidelli2005, Tsiganis2005, Gomes2005} was proposed by \cite{Nesvorny2007} and, in the specific case of Jupiter with the modern Nice model, by \citealp{Nesvorny2014}. In this scenario, during the early solar system instability, encounters between the outer planets occurred. These planetary encounters could exchange energy and angular momentum between planets and the objects nearby allowing the capture of irregular bodies by the giant planets. In this scenario, the survival rate of prior-LHB (Late Heavy Bombardment) satellites is very small.

Another possible mechanism is the capture through collisional interactions \citep{Sheppard2005}. A collision between two small bodies in the Hill's sphere of the planet could generate fragmented objects and the dissipated energy could be such that some of these objects could be captured.

Some of these objects are in dynamical groups with similar semi-major axis, eccentricities and inclinations, called families, similar to families found in the Main Asteroid Belt. These families may have been created by a parent body disrupted by collisions with comets or other satellites \citep{Nesvorny2004}. These collisions are more likely to have occurred during the LHB \citep{Gomes2005}.

@@

For Phoebe, ejected material from its surface caused by impacts could evolve due to Poynting-Robertson drag and collide with Iapetus causing the large variation in albedo observed on it \citep{Nesvorny2003}. Indeed, Cassini detected in Phoebe an absorption feature at 2.42 $\mu m$ (probably CN combinations) that was also detected in the dark side of Iapetus \citep{Clark2005}.

The region of origin of these object is not well known. \cite{Grav2003} and \cite{Grav2007} showed that the irregular satellites from the giant planets have their colors and spectral slopes similar to C-, D- and P-type asteroids, Centaurs and trans-neptunian objects (TNOs) suggesting that they come from different locations in the early solar system.

In order to obtain precise fundamental physical parameters like size, shape and albedo for the irregular satellites and thus to contribute to the study of their origin, we want to observe stellar occultations, which provide  more accurate results than other ground-based techniques \citep{Sicardy2011, Ortiz2012, Braga-Ribas2014}.

No observation of a stellar occultation by an irregular satellite was published up to date. Since their estimated sizes are very small (see Table \ref{Tab: satellite-diameter}), this may have prevented earlier tries. But, in fact, given their distances to us, current ephemeris and star positions are already good enough for the prediction of the exact location and instant where the shadow of the occultation will cross the Earth. For instance, Himalia, supposedly the largest irregular satellite of Jupiter has an estimated size of 150 km \citep{Porco2003}, which is equivalent to an apparent size of about 40 mas (milliarcseconds). Thus, in this case, the cumulated uncertainty of ephemeris and star position1 must be around 40 mas to get good chances of observing a stellar occultation, which is quite feasible today.

\begin{table}
\caption{\label{Tab: satellite-diameter} Estimated diameter of the satellites and correspondent apparent diameter}
\begin{centering}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Diameter of the satellites} \tabularnewline
Satellite  & mas\tablefootmark{a}  & km & References \tabularnewline
\hline
Ananke & 8 & 29 & 1 \tabularnewline
Carme & 13 & 46 & 1 \tabularnewline
Elara & 24 & 86 & 1 \tabularnewline
Himalia & 41 & $(150\times120) \pm 20$\tablefootmark{b} & 2 \tabularnewline
Lysithea & 10 & 36 & 1 \tabularnewline
Pasiphae & 17 & 62 & 1 \tabularnewline
Sinope & 10 & 37 & 1 \tabularnewline
\hdashline
Phoebe & 32 & $212 \pm 1.4$\tablefootmark{b} & 3 \tabularnewline
\hdashline
Nereid & 15 & $340 \pm 50$\tablefootmark{c} & 4 \tabularnewline
Triton & 124 & $2707 \pm 2.0$\tablefootmark{c} & 5 \tabularnewline
\hline
\end{tabular}
\tablebib{
(1) \cite{Rettig2001}; (2) \cite{Porco2003}; (3) \cite{Thomas2010}; (4) \cite{Thomas1991}; (5) \cite{Thomas2000}.}
\end{centering}
\tablefoottext{a}{Using a mean distance from Jupiter of 5 AU, from Saturn of 9 AU and from Neptune of 30 AU.}
\tablefoottext{b}{From Cassini observation.}
\tablefoottext{c}{From Voyager-2 observation.}
\par
\end{table}

From what we have just presented, we can think that the obsevation of an stellar occultation by an irregular satellite should be likelier than occultations by TNOs.. The orbits of their host planets are well known and their observation time-span covers many orbital periods, contrary to TNOs.
%Unlike stellar occultations by TNOs, which nevertheless have been proved effective, the observation of an occultation by a irregular satellite is, in principle, more favorable. The orbits of their host planets are well known and these satellites have been observed completing already many orbital periods around them, thus presenting better ephemeris than TNOs. 
Moreover, the irregular satellites are closer to Earth which means a minor localization error in kilometers.

\cite{GomesJunior2015} obtained 6523 suitable positions for 18 irregular satellites between 1992 and 2014 with an estimated error in the positions of about 60 to 80 mas. For some satellites the number of positions obtained is comparable to the number used in the numerical integration of orbits by the JPL \citep{Jacobson2012}. They pointed out that the ephemeris of the irregular satellites have systematic errors that may reach 200 mas for some satellites. For an object at the distance of Jupiter, this represents an error bigger than 700 km in the shadow path. Using the positions obtained by \cite{GomesJunior2015} we produced a specific ephemeris for short-time future for the satellites of Jupiter and better predict stellar occultations for these objects.

We present in this paper stellar occultation predictions for the 7 major irregular satellites of Jupiter (Himalia, Elara, Pasiphae, Lysithea, Carme, Ananke and Sinope), Phoebe from Saturn and Nereid and Triton from Neptune. In the section \ref{Sec: Rationale} we explore the scientific rationale for the study of the irregular satellites and the possibility of having a common origin with TNOs. In section \ref{Sec: integration} we show the the process of th productin of the new ephemeris. In section \ref{Sec: predictions}, we present the predictions of the stellar occultations by irregular satellites and how they were made. Some tests made to confirm the predictions are presented in section \ref{Sec: testes} and the final discussion are in section \ref{Sec: discussion}.

@@

Phoebe is the most studied irregular satellite. \cite{Clark2005} suggest that its surface is probably covered by material of cometary origin. It was also stated by \cite{Johnson2005} that if the porosity of Phoebe is 15\%, Phoebe would have an uncompressed density similar to those of Pluto and Triton.

\cite{Sheppard2005} and \cite{Jewitt2007} also expose the possibility for the irregular satellites having their origin as comets or TNOs. TNOs are highly interesting objects that, due to their large heliocentric distances, may be highly preserved having their physical properties similar to those they had when they were formed \citep{Camargo2014}. This is even more true for the smaller objects, since in principle larger sizes favour physical differentiation processes in the body and vice-versa. However, due to the distance, the smaller TNOs from this region are more difficult to observe. A clever way to overcome this difficulty is to study  the much closer irregular satellites, under the hypothesis that they share a common origin with the small TNOs' population.

Triton is a uncommon satellite. Its orbit is retrograde and inclined, but quasi-circular and very close to the planet compared to the irregular ones. Because Triton's orbit size is very small and its precession is not dominated by Solar perturbations, Triton is frequently excluded from the irregular satellites' class, but studied together by many authors \citep{Sheppard2005, Jewitt2007}.

Similarly to the irregular satellites, Triton was probably captured in the early solar system and may have the same origin as the TNOs \citep{Agnor2006}. Differently, Triton is bigger than the irregular satellites by an order of magnitude and has an atmosphere. The main motivation to study Triton by stellar occultations is to understand the evolution of its atmosphere due to Triton's complicated and extreme seasonal cycle \citep{McKinnon2007}.

@@

\section{Special tailored Ephemerides (STE) for Jupiter irregular satellites} \label{Sec: integration}

\subsection{Observations used}

The last observations used to develop JPL current ephemeris of the irregular satellites of Jupiter were obtained in 2012 \citep{Jacobson2012}. As a result, the errors on the residuals of recent observations are too important for the ephemeris to accurately predict stellar occultations without any corrections. In order to have efficient ephemerides for predicting the stellar occultations by irregular satellites, we need predictions based on recent observations. This is why we decided to develop our own ephemeris based on the observations published in \cite{GomesJunior2015}.

\cite{GomesJunior2015} published 6523 precise positions for 18 irregular satellites from observations made at the Observatório do Pico dos Dias (OPD), Observatoire Haute-Provence (OHP) and European Southern Observatory (ESO) between 1992 and 2014. %They showed that the orbits of the irregular satellites of the giant planets have systematic errors.
The offsets of the observations relative to the JPL ephemeris could be up to 200 mas for some satellites. %These differences could be associated with errors in their orbital elements.

@@

All the orbits determined for the satellites show satisfying residuals. %Yet, one of the satellites has a peculiar situation. Its small number of observations in our set means that its orbit is definitely loosely constrained. 
The residuals are lower than those obtained with JPL ephemeris, but the accuracy of an ephemeris decreases when we get further from the time of observations. The main risk of divergence over time comes from the possible absence of long-term effects when fitting to a short timespan of observations. If that were the case, our ephemeris would diverge too quickly to be of any use. JPL ephemerides are fitted over all the available observations. As a result, they will diverge less quickly than our own. Though they are no longer precise enough for our use, they remain a precious reference to identify whether our own model presents a quick divergence. We compared our ephemeris to the JPL for all the Jupiter satellites we fitted, until 2017. The divergence between 2015 and 2018 is at most \textit{\color{red}insert value here} for \textit{\color{red}insert right satellite name here}. A example of this difference for satellites Himalia and \textit{\color{red}whichever satellite you want, if you want)} is presented in Figure \ref{JPL-STE}.

@@

\begin{table*}
\caption{Initial osculating elements for Jupiter irregular satellites at JD 2451545.0. For Themisto's case, the small number of observations meant that the statistical uncertainty was even greater than the obtained elements, though the fitting proved satisfying. We decided to provide its elements with significant number comparable to the other satellite for information, but left it without uncertainty.  }\label{Tab: sat_ell}
\begin{center}
\begin{tabular}{ccccccc}
\hline\hline
Satellite & a (km) & e & incl. (EQJ2000) & $\Omega$ & $\omega$ & $v$ \\ 
\hline
Himalia &   11372100 $\pm$ 500    &    0.166 $\pm$ 0.002      &   45.14 $\pm$ 0.15      &   39.77 $\pm$ 0.19      &   351.48 $\pm$ 0.46      &   97.35 $\pm$ 0.48    \\
Elara &   11741170 $\pm$ 690  &      0.222 $\pm$ 0.002      &   28.64 $\pm$ 0.18      &   68.42 $\pm$ 0.43      &   179.82 $\pm$ 0.56      &   339.08 $\pm$ 0.82  \\
Pasiphae &  23425000  $\pm$ 5000    &     0.379  $\pm$ 0.001       &   152.44 $\pm$ 0.10      &   284.59 $\pm$ 0.21      &   135.96 $\pm$ 0.19      &   236.97 $\pm$ 0.16 \\
Sinope &   22968800 $\pm$ 5200   &     0.316 $\pm$ 0.002      &   157.76 $\pm$ 0.12      &   256.62 $\pm$ 0.55      &   298.38 $\pm$ 0.55      &   167.57 $\pm$ 0.19    \\
Lysithea &   11739900 $\pm$ 1300  &      0.136 $\pm$ 0.004      &    51.12 $\pm$ 0.27     &   5.53 $\pm$ 0.52      &   53.0 $\pm$ 1.5      &   318.9 $\pm$ 2.0   \\
Carme &   24202924 $\pm$ 4800      &  0.242 $\pm$ 0.001      &   147.13 $\pm$ 0.10      &   154.01 $\pm$ 0.25      &   47.90 $\pm$ 0.29      &   234.41 $\pm$ 0.19  \\
Ananke &  21683800  $\pm$ 7200  &     0.380 $\pm$ 0.002      &   172.29 $\pm$ 0.20      &   56.9 $\pm$ 1.2      &   123.3 $\pm$ 1.2      &   231.24 $\pm$ 0.21  \\
Leda &   11140300  $\pm$ 4300  &     0.173  $\pm$ 0.007     &   16.15  $\pm$ 0.75    &   272.6  $\pm$ 1.7    &   212.2  $\pm$ 3.6          &   218.8  $\pm$ 3.2  \\
%Themisto  & 7393800    &     0.198       &   25.77  &   220.0     &   216.3    &   262.1     \\
\hline
\end{tabular}

\end{center}
\end{table*}

@@

%\begin{figure*}
%\begin{centering}
%\subfigure[Offset from the JPL ephemeris]{\includegraphics[width=8.8cm]{figures/DEC_anom.png} \label{Fig:offxtanomxjpl}}
%\subfigure[\textcolor{red}{Offset from the numerical integration}]{\includegraphics[width=8.8cm]{figures/DEC_anom.png} \label{Fig:offxtanomxni}}
%\caption{Offsets of the declination of Carme by true anomaly from the JPL ephemeris and \textcolor{red}{from the numerical integration of the positions obtained in \cite{GomesJunior2015}}.
%\label{Fig:offxanom}}
%\end{centering}
%\end{figure*}

@@

The prediction of the occultations was made by crossing the stellar coordinates and proper motions of the UCAC4 catalogue \citep{Zacharias2013} with the special-tailored ephemeris for Jupiter satellites and JPL ephemeris for the others as presented in section \ref{Sec: integration}. The search for stellar candidates follows the same procedure as presented by \cite{Assafin2010, Assafin2012} and \cite{Camargo2014}.

@@

A total of 588 events \textcolor{red}{(Not counting Triton's event yet)} were identified between January 2015 and December 2017. Table \ref{Tab: occ-list} shows a sample of the catalogue of occultations generated and their parameters, which are necessary to produce occultation maps (see Fig. \ref{Fig: ocultacao} as an example). Since these objects are very small, the duration of each event is a few seconds.

\begin{table*}
\caption{\label{Tab: sample-cds} Stellar occultation sampled predictions for Himalia \textcolor{red}{I still have to fix the table}}
\begin{centering}
\begin{tabular}{ccccccccccccccccccccccc}
\hline 
%\multicolumn{9}{c}{Himalia} \tabularnewline
\hline
% & \multicolumn{2}{c}{Mean errors} & Nr & Nr &  UCAC4       \tabularnewline
d m Year & h m s & \multicolumn{2}{c}{RA (ICRS) Dec} & C/A & P/A & v & D & R* & $\lambda$ & LST & $\Delta e_{\alpha *}$ & $\Delta e_{\delta}$ & pm & ct & $E_{\alpha *}$ & $E_{\delta}$ & $\mu_{\alpha *}$ & $\mu_{\delta}$ \tabularnewline
\hline
 07 10 2015 & 21 52 34. &  10 53 40.1835 & +08 21  00.489 & 0.465 & 200.31 & 39.31 & 6.25 & 16.6 & 179. & 09:48 & -31.0 & -13.0 & ok & uc &   0  &  0 & -13 &  -7 \tabularnewline
 23 10 2015 & 07 54 50. &  11 05 26.6037 & +07 14  32.030 & 1.017 & 201.33  & 36.11 & 6.12 & 15.5 & 16. & 08:59 & -31.0 & -13.0 & ok & uc &  0  &  0 &  -7 &  -4 \tabularnewline
 31 10 2015 & 00 24 19. &  11 10 56.2964 & +06 42  07.110 &  1.801 &  21.84 & 33.94 &  6.04 & 16.9 &  123. & 08:34 & -31.0 & -13.0 & ok & uc & 0  &  0 & -4 & -13 \tabularnewline
 07 11 2015 &  21 22 53. &  11 16 14.3041 & +06 10  05.194 &  0.306 &  202.36 & 31.33 & 5.94 & 16.2 & 162. & 08:09 & -31.0 & -13.0 & ok & uc & 0 & 0 & 0 & 0 \tabularnewline
 08 11 2015 & 04 27 21. &  11 16 25.7881 & +06 08  55.566 & 1.077 & 202.38 & 31.23 & 5.94 & 16.9 & 55. & 08:08 & -31.0 & -13.0 & ok & uc & 0 & 0 & 9 & -10 \tabularnewline
% 09 11 2015  09 01  4.   11 17 11.6890 +06 04  11.474   11 17 11.7030 +06 04  11.980   0.549   22.45  30.79  5.92 15.9  0.5  0.5  0.5   346. 08:04     -31.0    -13.0 ok uc 0    0    0   19  -13 \tabularnewline
% 11 11 2015  12 58 46.   11 18 33.8286 +05 55  43.695   11 18 33.8357 +05 55  43.946   0.274   22.59  29.98  5.90 14.6  0.4  0.4  0.4   285. 07:57     -31.0    -13.0 ok uc 0    0    0  -14    1 \tabularnewline
% 12 11 2015  20 14 22.   11 19 22.2740 +05 50  40.732   11 19 22.3183 +05 50  42.312   1.713   22.68  29.48  5.88 15.7  0.4  0.4  0.4   175. 07:52     -31.0    -13.0 ok uc 0    0    0   -7   -4 \tabularnewline
% 04 12 2015  03 31 56.   11 30 41.9967 +04 37  36.039   11 30 42.0020 +04 37  36.217   0.196   24.18  20.14  5.56 15.0  0.0  0.0  0.0    47. 06:40     -31.0    -13.0 ok uc 0    0    0    5   -9 \tabularnewline
\hline
\end{tabular}
\par\end{centering}
